Examples Compendium

### 2021-01-10 examples.tex
spewed cycles
Rogers adds

Take 2: Let's try different weights.
\[
\begin{aligned}
    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
    \mu &= (2,2,1) & \lambda &= (4,1,0)
\end{aligned}    
\]
and 
\[
\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
    0 & 1 & 0 & 0 & 0\\
    0 & s & A_0 & A_1 & A_2\\
    0 & 0 & 0 & 1 & 0\\
    0 & 0 & 0 & s & A_3\\
    0 & 0 & 0 & 0 & s
    \end{BMAT}\right]
\]
We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$. Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by 
$$
\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
$$ 
or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
Finally $E_s$ is spanned by an additional 1-cycle 
$$
e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
$$
assuming $A_3 = 0$ and $A_2 = 0$. Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$. 
This gives us 
\[
    \young(12) \ast \young(12,3) = (A_2,A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
\]  
Does it agree with what is expected on the module/cluster side? 
\[
S_1 \ast (1\to 2) = S_1 \oplus (1 \to 2) \qquad S_1 \ast (1\leftarrow 2) = S_1 \oplus (1 \leftarrow 2)
\]
The MV cycle of $\young(12)$ is a $\PP^1$: via MVy it has an open subset comprised of matrices 
\[
    \left[\begin{BMAT}(e){c;c}{c;c} 
        0 & A_0\\
        0 & 0
        \end{BMAT}\right] : A_0\ne 0
\]
The MV cycles of the other two tableaux are made up of matrices of the form 
\[
    \left[\begin{BMAT}(e){c;c;c}{c;c;c} 
        0 & A_0 & A_1\\
        0 & 0 & A_2\\
        0 & 0 & 0
        \end{BMAT}\right] : 
        \begin{cases}
            A_0 \ne 0 \text{ and } A_2 = 0 & \tau = \young(12,3) \\
            A_0 = 0 \text{ and } A_2 \ne 0 & \tau = \young(13,2)
        \end{cases} 
\] both $\CC^2$'s. \acom{How do the coordinates relate?}
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\newpage
\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

@@

Now consider the case that the young diagram we are working with is $\tau_2$. Then we have $e_4 + se_5$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix. We find that the 2-cycle is
\[
\left\{e_4 + se_5, -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
\]
and this requires that $ae - s^2c = 0$.

@@

For the remaining 2-cycle, we note that $e_4 + se_5 \notin \col(X-sI)$ but $e_6 \in \col(X-sI)$ so our 2-cycle is
\[
\left\{ e_6, \frac{1}{g} e_7 \right\}
\]
which requires $d = 0$ and $f = 0$.

From the minimal polynomial, we have $X^2 (X-sI)^2 = 0$ which gives us the equations
\[
a+sb = cs+eb = bf+cg+ds = esg = 0.
\]
Taking $s\rightarrow 0$, we have the following equations for our two cases of $\tau_2$ and $\tau'_2$:
\[
\begin{array}{c|c}
    \tau_2 & \tau'_2 \\ \hline
    a = 0 & a = 0 \\
    g = 0 & c = 0 \\
    eb = 0 & d = 0 \\
    bf = 0 & e = 0 \\
    ed-cf = 0 & f = 0
\end{array}
\]

@@

However for the $\tau'_2$ case, the coordinate ring is 
\[
\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,d,e,f \rangle}
\cong \CC[b,g]
\]
which corresponds to $\AA^2$. Since $\tau'_2$ corresponds to the module $2\leftarrow 3$, we expect two irreducible components corresponding to the modules $P_3 = 1 \leftarrow 2 \leftarrow 3$ and $1 \rightarrow 2 \leftarrow 3$. $P_3$ corresponds to the variety $Gr(3,4) \cong \PP^3$ and $1 \rightarrow 2 \leftarrow 3$ also corresponds to a toric variety whose polytope is a square-based pyramid (?).
\end{example}
\end{document}

>>>>

Take 2: Let's try different weights.
\[
\begin{aligned}
    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
    \mu &= (2,2,1) & \lambda &= (4,1,0)
\end{aligned}    
\]
and 
\[
\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
    0 & 1 & 0 & 0 & 0\\
    0 & s & A_0 & A_1 & A_2\\
    0 & 0 & 0 & 1 & 0\\
    0 & 0 & 0 & s & A_3\\
    0 & 0 & 0 & 0 & s
    \end{BMAT}\right]
\]
We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$. Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by 
$$
\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
$$ 
or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
Finally $E_s$ is spanned by an additional 1-cycle 
$$
e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
$$
assuming $A_3 = 0$.
% and $A_2 = 0$?? 
Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$.
% and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$??
This gives us 
\[
    \young(12) \ast \young(12,3) = (A_3) \qquad % A_2, 
    \young(12) \ast \young(13,2) = (A_0 + sA_1) \to (A_0) %  , A_3
\]  
Does it agree with what is expected on the module/cluster side? 
\[
S_1 \ast (1\to 2) = S_1 \oplus (1 \to 2) \qquad S_1 \ast (1\leftarrow 2) = S_1 \oplus (1 \leftarrow 2)
\]
The MV cycle of $\young(12)$ is a $\PP^1$: via MVy it has an open subset comprised of matrices 
\[
    \left[\begin{BMAT}(e){c;c}{c;c} 
        0 & A_0\\
        0 & 0
        \end{BMAT}\right] : A_0\ne 0
\]
The MV cycles of the other two tableaux are made up of matrices of the form 
\[
    \left[\begin{BMAT}(e){c;c;c}{c;c;c} 
        0 & A_0 & A_1\\
        0 & 0 & A_2\\
        0 & 0 & 0
        \end{BMAT}\right] : 
        \begin{cases}
            A_0 \ne 0 \text{ and } A_2 = 0 & \tau = \young(12,3) \\
            A_0 = 0 \text{ and } A_2 \ne 0 & \tau = \young(13,2)
        \end{cases} 
\] both $\CC^2$'s. \acom{How do the coordinates relate?}
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\newpage
\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

@@

Now consider the case that the young diagram we are working with is $\tau_2$. Then we have $e_4 + se_5 + x(e_1 + se_2 + s^2e_3)$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix. We find that the 2-cycle is
\[
\left\{e_4 + se_5 + x(e_1 + se_2 + s^2e_3), -\frac{2x}{s}e_1 -xe_2 -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
\]
and this requires that $ae - s^2c = 0$.

@@

For the remaining 2-cycle, we want it to end with $x(e_1 + se_2 + s^2e_3) + (e_4 + se_5) + ye_6$ so our 2-cycle is
\[
\left\{ x(e_1 + se_2 + s^2e_3) + (e_4 + se_5) + ye_6, -\frac{2x}{s}e_1 -xe_2 -\frac{1}{s}e_4 +\frac{s}{f} e_7\right\}
\]
which requires $af-ds^2=0$ and $fy-sg = 0$. As $y$ is free, the last equation is not really a restriction on $f$ and $g$.

From the minimal polynomial, we have $X^2 (X-sI)^2 = 0$ which gives us the equations
\[
a+sb = cs+eb = bf+cg+ds = esg = 0.
\]
Taking $s\rightarrow 0$, we have the following equations for our two cases of $\tau_2$ and $\tau'_2$:
\[
\begin{array}{c|c}
    \tau_2 & \tau'_2 \\ \hline
    a = 0 & a = 0 \\
    g = 0 & c = 0 \\
    eb = 0 & e = 0 \\
    bf = 0 & bf = 0 \\
    ed-cf = 0 & 
\end{array}
\]

@@

However for the $\tau'_2$ case, the coordinate ring is 
\[
\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,e,df \rangle}
\cong \frac{\CC[b,d,f,g]}{\langle df \rangle}
\]
which corresponds to $\AA^3 \cup \AA^3$. Since $\tau'_2$ corresponds to the module $2\leftarrow 3$, we expect two irreducible components corresponding to the modules $P_3 = 1 \leftarrow 2 \leftarrow 3$ and $1 \rightarrow 2 \leftarrow 3$. $P_3$ corresponds to the variety $Gr(3,4) \cong \PP^3$ and $1 \rightarrow 2 \leftarrow 3$ also corresponds to a toric variety whose polytope is a square-based pyramid (?).
\end{example}

\begin{example}[Above example redone]
    In $\CC[A_0..A_6]$ where 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c} 
            0 & 1 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
            0 & 0 & 0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & 0 & s & A_4 & A_5\\
            0 & 0 & 0 & 0 & 0 & s & A_6\\
            0 & 0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    
    \]
    we have 
    $$
    \begin{aligned}
        \young(12)*\young(11,23,4) &= ({\color{blue}A_6,A_2A_5-A_3A_4},A_1A_4 + A_2s,A_1s + A_0) \\
        &= (A_6,A_2A_5 - A_3A_4, A_1A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_4,A_5,A_6) \sqcup (A_0,A_1,A_6,A_2A_5 - A_3 A_4) \sqcup (A_0,A_2,A_4,A_6)
    \end{aligned}
    $$ 
    while 
    $$
    \begin{aligned}
        \young(12)*\young(11,24,3) &= ({\color{blue}sA_0A_5 + (1 + s^2)A_1A_5+sA_3},A_2,A_4,A_1s + A_0) \\
        &= (A_1A_5,A_2,A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_2,A_4,A_5) \sqcup (A_0,A_1,A_2,A_4) 
    \end{aligned} 
    $$
    Cycles are 
    \[
    \frac{A_0}{s^2}e_2 + e_4 \xrightarrow{A} e_1    
    \]
    and, in the $\young(11,23)$ case, 
    \[
    \begin{aligned}
        e_2 + 2s e_3 \xrightarrow{A-s} e_1 + se_2 + s^2 e_3 \\
        (sA_4 e_4 + (1 + s^2)A_4 e_5 + se_6)/(sA_4) \xrightarrow{A-s} (e_4 + se_5)/s 
    \end{aligned}    
    \]
    while in the $\young(11,2,3)$ case,
    \[
        \begin{aligned}
      e_6 \xrightarrow{A-s} 0 \\
      e_4 + (1/s + s) e_5 + (1/A_5) e_7 \xrightarrow{A-s} (1/s)e_4 + e_5 + \ast e_6   
        \end{aligned}
    \]
\end{example}
\end{document}
